Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-11-29 Tex/Old text/chapters/introduction.tex
Thesis update

>>>>

It is worth mentioning that we decided, in agreement and with the consent of the coordination of the postgraduate program, that this document would be written in active voice and entirely in English. The choice of the passive voice comes from the choice of the English language, which in the studied thesis always always presented in active voice. On the other hand, the choice of language comes from the possibility that the research may lead to further developments and activities, without the need for translation.
